\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{What is the significance of this photo? Why does it exist?}
Photographs serve as a vivid, undebatable view into the past. In some cases, they can serve as reminders of times past, or of the good in humans. However, the image that I've chosen serves to be neither of those things: it is a view into the brutal reality of the past. This image was taken in the slums of the Philippines, off the corner of one of the busiest streets there, and it shows a dead man in the corner, with an investigation crew in the background. This horrifying scene was caused by a surprisingly large part of society: drugs. 

More specifically, this image shows the effects of the "War on Drugs" on society. In the 1990s, former president Richard Nixon declared "public drug abuse: public enemy No. 1," sparking an unprecedented global campaign to eradicate not drugs, but drug \textit{users}, through incarceration and punishment; the aim was to decrease the amount of drugs by decreasing drug use. However, this violated a very fundamental law of business: supply and demand. Drug users will do  \textit{anything} to get their fix, no matter how illegal or hard-to-get they are. As a result, the government and drug sellers locked horns, each becoming more and more violent, driving up prices for drugs, until \textit{direct} harm started to come to the citizens who cannot, which is what this photo shows.

The Philippines have killings on an almost daily bases, from people of all walks of life: from a \textit{5-year-old child}, to the family of a 72-year-old, and it is images like this that bring awareness to individuals, and they make impact. Globally, the "War on Drugs" has been deemed a complete waste of money, time, and resources. Talks are being resumed about a more humane approach to drug use and abuse, which I believe is a much-needed alternative. Slowly but surely, the world is shifting their view on drugs for the better, and if not for horrifying but \textit{real} photos like this one, our world would be the worse for it.

\end{document}